Realizability-Preserving DG-IMEX Method for the Two-Moment Model of Fermion Transport \tnoteref{support}

### 2018-04-02 Documents/M1/realizableFermionicM1/sections/appendix.tex
Added more description for IMEX PA2+.
Added the details of IMEX PC2.

We here give another second-order accurate, sitivity-preserving IMEX scheme of type $A$, named IMEX PA2+, which has a lager $c_{sch}$ than IMEX PA2.
It was chosen from $10^{6}$ coefficient groups that satisfy both the second-order accuracy requirement and the positivity-preserving requirement.
IMEX PA2+ is the one has the largest ($C_{sch} = 0.895041066934$). Its non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.909090909090909, \nonumber \\
  \tilde{a}_{31} &= 0.450000000000000, \quad \tilde{a}_{32} = 0.550000000000000, \nonumber \\
  a_{11} &= 0.521932391842510, \nonumber \\
  a_{21} &= 0.479820781424967, \quad a_{22} = 0.002234534340252, \nonumber \\
  a_{31} &= 0.499900000000000, \quad a_{32} = 0.001100000000000, \quad a_{33} = 0.499000000000000. \nonumber
\end{align}
The coefficient in the correction step is $\alpha = 0.260444263529413$.  
\paragraph{IMEX PC2}

>>>>

We here give another second-order accurate, sitivity-preserving IMEX scheme of type $A$, named IMEX PA2+, which has a lager $c_{sch}$ than IMEX PA2.
It was chosen from $10^{6}$ coefficient groups that satisfy both the second-order accuracy requirement and the positivity-preserving requirement.
IMEX PA2+ is the one has the largest ($c_{sch} = 0.895041066934$). 
Its non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.909090909090909, \nonumber \\
  \tilde{a}_{31} &= 0.450000000000000, \quad \tilde{a}_{32} = 0.550000000000000, \nonumber \\
  a_{11} &= 0.521932391842510, \nonumber \\
  a_{21} &= 0.479820781424967, \quad a_{22} = 0.002234534340252, \nonumber \\
  a_{31} &= 0.499900000000000, \quad a_{32} = 0.001100000000000, \quad a_{33} = 0.499000000000000. \nonumber
\end{align}
The coefficient in the correction step is $\alpha = 0.260444263529413$.  
This scheme is also a GSA scheme: $\tilde{w}_{i}=\tilde{a}_{3i}$ and $w_{i}=a_{3i}$ for $i\le3$.

\paragraph{IMEX PC2}

A second-order accurate, positivity-preserving, diffusion accurate IMEX scheme was given in \cite{mcclareen_2008}.  
We refer to this scheme as IMEX PC2.  
Its non-zero components of $\tilde{A}$ and $A$ are given by
\begin{align}
  \tilde{a}_{21} &= 0.5, \nonumber \\
  \tilde{a}_{32} &= 1, \nonumber \\
  a_{22} &= 0.5, \nonumber \\
  a_{33} &= 1.0. \nonumber
\end{align}
And $\tilde{w}_{i}=\tilde{a}_{3i} = w_{i}=a_{3i}$ for $i\le3$.
A common choice of this scheme is $c_{sch} = 0.3$.
